---
title: "Introduction to plinkr"
author: "Alvaro Franquet"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

require(dplyr)
require(plinkr)
```

`plinkr` allows you to manage [PLINK](https://www.cog-genomics.org/plink2) in R 
using dplyr's style syntax. Take a look at an example.

```{r, eval = FALSE}

plinkr() %>% 
  file('path/to/file') %>%
  freq() %>%
  out('path/to/output_dir')

```

## Installation and configuration

To use this package you need to install [PLINK](https://www.cog-genomics.org/plink2)
first.

You can install the latest development version from GitHub.
The easiest way to do that is by using `devtools`.

```{r, eval = FALSE}
library(devtools)
devtools::install_github(repo = 'alvarofranq/plinkr')
```

Once you have `plinkr` installed you need to indicate the `PLINK_HOME` path using:

```{r}
Sys.setenv('PLINK_HOME' = 'plink')
```

New command example: 

```{r}

plinkr() %>%
  bfile('path/to/file') %>%
  make_bed() %>%
  out('output/path')

```
